### 2021-08-29 documentos/pce.tex
respuesta
bibliografia
avance

\section{PCE Maps} % {{{
\subsection{Quantum channels}
\subsection{Single qubit case} % {{{
% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
% mapas proyectivos, hay mapas proyectivos no unitales}
\todo{David escribe una primera version y luego Carlos itera}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}

>>>>

\section{PCE Maps} % {{{
\subsection{Quantum channels}
Quantum channels comprehend the most general linear operations that a quantum system undergo independently of its past~\cite{zimansbook,cirac}. To introduce their construction and properties, first let us define several objects. We will denote Hilbert spaces as \hilbert and $d$-dimensional Hilbert spaces as $\hilbert_d$. The set of bounded operators over a Hilbert space \hilbert will be written as $\mcB(\hilbert)$, the subset of density matrices as $\mcS(\hilbert)$, which is in turn a subset of the so called trace-class operators $\mcT(\hilbert)$, for the finite dimensional case, the one studied here, $\mcT(\hilbert)$ and $\mcB(\hilbert)$ coincide~\cite{zimansbook}.

Their construction include basically three ingredients: linearity, trace preserving and complete positivity.The first one is needed to send convex combinations of density matrices into the convex combination of the evolution of such density matrices, this is, let $\mcE$ such linear operation, thus $p \rho_1 +(1-p) \rho_2 \mapsto p \mcE[\rho_1]+(1-p)\mcE[\rho_2]$
\subsection{Single qubit case} % {{{
% \ddnote{Sugiero otro nombre para esta seccion, pues los PCE no son los unicos
% mapas proyectivos, hay mapas proyectivos no unitales}
\todo{David escribe una primera version y luego Carlos itera}
\begin{itemize}
\item The single qubit case, describe some of the features.
\item Single qubit Kraus operators.
\item Single qubit relation with decoherence. 
\end{itemize}
% }}}
\subsection{Pauli component erasing maps} % {{{
\begin{itemize}
\item Give a formal definition of the PCE \todo{Jose Alfredo escribe}
\item Give some two qubit examples to illustrate non-trivial points with examples
(isualizacion y ejemplos)
\todo{Jose Alfredo escribe}
\item Canales de Ruskai Pauli maps, que la interseccion es no trivial (no estan contenidos en ninguna direccion, pero la interseccion es no vacia)
y Relación con canales citados en \cite{Siudzinska2020}? \cpnote{Esto quiza lo tengamos
que mover si es que necesitamos herramientas que discutiremos mas adelante para
hacer notar la diferencia}
\end{itemize}
% }}}
% \begin{itemize}
% \item Son positivas todas las matrices de densidad que resultan de aplicar un
% mapeo no válido? \janote{Creo que sí.  Para 1 qubit aplicar PCEs no CP siempre
% te deja dentro de la esfera de Bloch.  Así que estoy casi seguro que lo mismo
% sucede para $n$ qubits.}
% \end{itemize}
% }}}
